---
title: "Pearson analysis"
author: "£ukasz Królik"
date: "31 stycznia 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction 
Process of learning foreign languages has been changed for the last few years. Earlier the most important medium of learning were books, but progress of technology supplied a new tools - the process is more efficient by creating an interactive excersises which are based on multimedial content - such as audio, video. One of most popular publishing house in the world - Pearson also had adjusted to this trend and started to create educational content as "E-learning". Process of collecting, processing and analysing data gathered from users can help developers to create better products. This report tries to find knowledge in sample dataset from users. 

# Processing data 

#### Importing libraries
```{r importLibraries,  warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(stargazer)
```
#### Kod pozwalaj¹cy wczytaæ dane z pliku.
```{r loadFromFile, warning=FALSE, message=FALSE, error=FALSE}
setwd("D:/pearson")
tabAll <- read.csv("data2018.csv",sep=";",na.strings = "")
colnames(tabAll)[1] <- "learner_id"
```
#### Handling problems with missing values and outliers
Imported dataset had some NA values in attributes Fortunately set of rows with NA values wasn't too large, so it was removed. Another problems were outliers - some rows with average score and inv_rate were much bigger than normal - what made a problem with visualization. This rows also were dropped. 

Finally, it was necessary to reorder Unit column, because it was sorted alfabetically by default - and it was wrong approach. Real order is different - firstly 3 units of excersises and then a review.  
```{r findMissingValues,  results='asis'}
#missing values
knitr::kable(sapply(tabAll, function(x) sum(is.na(x))))
```

```{r handleMissingValues}
#missing values
tabCleaned <- tabAll %>% drop_na() %>% filter(avg_score <= 1) %>% filter(inv_rate <= 1)
#binning of scores to buckets
tabCleaned["mark"] <- cut(tabCleaned$avg_score,breaks = c(-0.1,0.5,0.7,0.85,0.98,1), labels = c("very bad","bad","medium","good","excellent"))
print(summary(tabCleaned))
```
## Tworzenie tematycznych tabel podsumowuj¹cych zbiór
```{r createSummaries, cache= TRUE}
countrySummary <- tabCleaned %>% group_by(country, in_course) %>% summarise(avg_completion = mean(completion),avg_score = mean(avg_score), inv_rate= mean(inv_rate), nlearners = length(unique(learner_id))) %>% arrange(-nlearners) %>% filter(nlearners > 30)
p <- ggplot(data = countrySummary, aes(x= country, y = nlearners))
p + geom_bar(stat="identity")

unitSummary <- tabCleaned %>% group_by(unit, in_course) %>% summarise(avg_scores = mean(avg_score), n = n(), avg_compl = mean(completion))
p <- ggplot(data = unitSummary, aes(x= unit, y = n, fill = avg_compl))
p + geom_bar(stat= "identity")  + geom_label(label =  "2")

bottom1percentSummary <- tabCleaned %>% group_by(learner_id, country, in_course) %>% summarise(avg_scores = mean(avg_score), n = n(), inv_rate = mean(inv_rate)) %>% arrange(avg_scores)
p <- ggplot(data = bottom1percentSummary, aes(x = learner_id, y = avg_scores, color = in_course))
p + geom_point()

```

## Dataset and attributes
Cleaned dataframe contains `r nrow(tabCleaned)` rows and `r ncol(tabCleaned)` attributes.
```{r basicStats, results='asis'}
knitr::kable(summary(tabCleaned))

```

#### Learner_id
it is an identificator of person who is taking part in learning process. This dataframe contains information about `r length(unique(tabCleaned$learner_id))` students.

#### Country
it is a country of learner. In this context students are from `r length(unique(tabCleaned$country))` countries. This table presents 10 countries which are mostly represented by platform users.
`r knitr::kable(countrySummary %>% group_by(country) %>% summarise(nlearners = sum(nlearners)) %>%  arrange(-nlearners) %>% head(10) )`

#### In_course
Learners can take part in course with teacher, or alone. More students was taught with teacher.

#### Unit

#### Avg_score

#### Completion

#### Inv_rate


## Szczegó³ow¹ analizê wartoœci atrybutów (np. poprzez prezentacjê rozk³adów wartoœci).
```{r showCorrelations, cache= TRUE}
#library(polycor)
#library(reshape)
#library(sjPlot)
#library(polycor)
library(GGally)
#tabToCor <- tabCleaned %>% select(-learner_id)
#tabToCor[] <- lapply(tabToCor,as.integer)
#sjp.corr(tabToCor)
#d_cor <- as.matrix(hetcor(tabCleaned))
#d_cor_melt <- arrange(melt(d_cor), -abs(value))
print(1+1)
ggpairs(tabCleaned %>% select(-country, -unit, -learner_id),  mapping=ggplot2::aes(colour = mark))
#d_cor_filtered <- d_cor_melt %>% filter(Var2 == 'kwh') %>%  head(6)
```

## Sekcjê sprawdzaj¹c¹ korelacje miêdzy zmiennymi; sekcja ta powinna zawieraæ jak¹œ formê graficznej prezentacji korelacji.
```{r showCorrelations, cache= TRUE}
#library(polycor)
#library(reshape)
#library(sjPlot)
#library(polycor)
library(GGally)
#tabToCor <- tabCleaned %>% select(-learner_id)
#tabToCor[] <- lapply(tabToCor,as.integer)
#sjp.corr(tabToCor)
#d_cor <- as.matrix(hetcor(tabCleaned))
#d_cor_melt <- arrange(melt(d_cor), -abs(value))
print(1+1)
ggpairs(tabCleaned %>% select(-country, -unit, -learner_id),  mapping=ggplot2::aes(colour = mark))
#d_cor_filtered <- d_cor_melt %>% filter(Var2 == 'kwh') %>%  head(6)
```
# Data analysis

#### Wp³yw wspó³czynnika completion na dane

#### Wp³yw wspó³czynnika country na dane

#### Wp³yw wspó³czynnika inv_rate na dane

#### Wp³yw wspó³czynnika in_course na dane

## Interaktywny wykres lub animacjê prezentuj¹c¹ zmianê wytwarzanej energii w czasie i przestrzeni.

## Wnioski
